Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
wip

\noindent
\textbf{The charging scheme.}
We charge both \OPT and \RM whenever \RM collocates a~pair.%(i.e., on a~collocation event).
\RM collocates a~pair always with a~swap,%(i.e., two simultaneous migrations),
which  costs $2\alpha$,
while \OPT may save some costs by collocating multiple pairs at once.
% before they inflict too much communication cost.
 Thus it pays the price of only one migration per pair  (see Figure \ref{fig:cyclic}).
Whenever \OPT collocates a~pair,
we charge it only the cost $\alpha$ of moving a~single node to the other cluster (in contrast to the cost $2\alpha$ incurred by \RM).

>>>>

\noindent
\textbf{The charging scheme.}
We charge both \OPT and \RM whenever \RM collocates a~pair.%(i.e., on a~collocation event).
\RM collocates a~pair always with a~swap,%(i.e., two simultaneous migrations),
which  costs $2\alpha$,
while \OPT may save some costs by collocating multiple pairs at once.
% before they inflict too much communication cost.
 Thus it pays the price of only one migration per pair  (see Figure \ref{fig:cyclic}).
For this reason, whenever \OPT collocates a~pair,
we charge it only the cost $\alpha$ of moving a~single node to the other cluster (in contrast to the cost $2\alpha$ incurred by \RM).
